%\newcites{}{Bibliography}

%\addcontentsline{toc}{chapter}{\textit{Bibliography}}
\addcontentsline{toc}{chapter}{{Bibliography}}

\renewcommand{\bibname}{{Bibliography}}

\begin{thebibliography}{99}

\bibitem{e}
Bayly, P. V., and L. N. Virgin. “An Empirical Study of the Stability of Periodic Motion in the Forced Spring-Pendulum.” \emph{Proceedings: Mathematical and Physical Sciences}, vol. 443, no. 1918, 1993, pp. 391–408. JSTOR, \url{www.jstor.org/stable/52258}. Accessed 2 Aug. 2021.

\bibitem{n}
Craig, K. “Spring-Pendulum Dynamic System.” \emph{NYU Engineering}, \url{engineering.nyu.edu/mechatronics/Control\_Lab/Criag/Craig\_RPI/200}. Accessed 2 Aug. 2021.

\bibitem{m}
“Classical Mechanics | Lecture 3.” \emph{YouTube}, uploaded by Stanford, 16 Dec. 2011, \url{www.youtube.com/watch?v=3apIZCpmdls}.

\bibitem{b}
Digilov, Rafael M., et al. “Damping in a Variable Mass on a Spring Pendulum.” \emph{American Journal of Physics}, vol. 73, no. 10, 2005, pp. 901–05. \emph{Crossref}, doi:10.1119/1.1979498.

\bibitem{r}
“Equations of Motion for the Elastic Pendulum (2DOF) Using Lagrange’s Equations.” \emph{YouTube}, uploaded by Good Vibrations with Freeball, 10 July 2020, \url{www.youtube.com/watch?v=iULa9A00JpA}.

\bibitem{a}
Girgin, Z., and E. Demir. \emph{Investigation of Elastic Pendulum Oscillations by Simulation Technique}. Journal of Engineering Sciences, 2009, \url{jag.journalagent.com/pajes/pdfs/PAJES_15_1_81_86.pdf}.

\bibitem{y}
Han, Yün. “ECE 486 Control Systems.” \emph{ECE 486 Control Systems - Lecture 2}, University of Illinois, 18 Jan. 2018, \url{courses.engr.illinois.edu/ece486/sp2021/documentation/handbook/lec02.html}.

\bibitem{x}
“Hamilton’s Principle and Euler-Lagrange Equations.” \emph{YouTube}, uploaded by Rangeet Bhattacharyya, 15 Sept. 2020, \url{www.youtube.com/watch?v=FBcS9RHzHRw}.

\bibitem{z}
“Introduction to Lagrangian Mechanics.” \emph{YouTube}, uploaded by Physics Explained, 18 Oct. 2020, \url{www.youtube.com/watch?v=8UtnDaGHpq0}.

\bibitem{ac}
Libretexts. “10.4: Rayleigh’s Dissipation Function.” \emph{Physics LibreTexts}, 28 Feb. 2021, \url{phys.libretexts.org/Bookshelves/Classical\_Mechanics/ \\ Variational\_Principles\_in\_Classical\_Mechanics\_(Cline)/ \\ 10\%3A\_Nonconservative\_Systems/10.04\%3A\_Rayleighs\_Dissipatio\_Function}.

\bibitem{d}
Minguzzi, E. “Rayleigh’s Dissipation Function at Work.” \emph{European Journal of Physics}, vol. 36, no. 3, 2015, p. 035014. \emph{Crossref}, doi:10.1088/0143-0807/36/3/035014.

\bibitem{ax}
Pokorny, P. “Continuation of Periodic Solutions of Dissipative and Conservative Systems: Application to Elastic Pendulum.” \emph{Mathematical Problems in Engineering}, vol. 2009, 2009, pp. 1–15. Crossref, doi:10.1155/2009/104547.

\bibitem{ak}
“Rayleigh Dissipation Function | Classical Mechanics | LetThereBeMath |.” \emph{YouTube}, uploaded by Let there be math, 24 Oct. 2017, \url{www.youtube.com/watch?v=AX\_XjLxTXWU}.

\bibitem{ap}
Stanovnik, Aleš, and Borut Jurcic-Zlobec. “Numerical Study of the Elastic Pendulum on the Rotating Earth.” \emph{ISRN Mathematical Physics}, vol. 2012, 2012, pp. 1–7. \emph{Crossref}, doi:10.5402/2012/806231.

\bibitem{am}
“Showcase of Lagrangian Mechanics Using an Elastic Pendulum.” \emph{YouTube}, uploaded by Benedict Wesson, 24 May 2015, \url{www.youtube.com/watch?v=CA34i245meQ}.

\bibitem{bf}
Wylie, Clarence Raymond. \emph{Advanced Engineering Mathematics}. 4th ed., McGraw-Hill, 1975.

\bibitem{h}
Zammit, Corey, et al. \emph{The Dynamics Of The Elastic Pendulum}. Tucson, University of Arizona, 2018.

%\bibitem{a}
%Girgin, Z., and E. Demir. \emph{Investigation of Elastic Pendulum Oscillations by Simulation Technique}. Journal of Engineering Sciences, 2009, \url{jag.journalagent.com/pajes/pdfs/PAJES_15_1_81_86.pdf}.

%\bibitem{b}
%Digilov, Rafael M., et al. “Damping in a Variable Mass on a Spring Pendulum.” \emph{American Journal of Physics}, vol. 73, no. 10, 2005, pp. 901–05. \emph{Crossref}, doi:10.1119/1.1979498.

%\bibitem{d}
%Minguzzi, E. “Rayleigh’s Dissipation Function at Work.” \emph{European Journal of Physics}, vol. 36, no. 3, 2015, p. 035014. \emph{Crossref}, doi:10.1088/0143-0807/36/3/035014.

%\bibitem{e}
%Bayly, P. V., and L. N. Virgin. “An Empirical Study of the Stability of Periodic Motion in the Forced Spring-Pendulum.” \emph{Proceedings: Mathematical and Physical Sciences}, vol. 443, no. 1918, 1993, pp. 391–408. JSTOR, \url{www.jstor.org/stable/52258}. Accessed 2 Aug. 2021.

%\bibitem{h}
%Zammit, Corey, et al. \emph{The Dynamics Of The Elastic Pendulum}. Tucson, University of Arizona, 2018.

%\bibitem{m}
%“Classical Mechanics | Lecture 3.” \emph{YouTube}, uploaded by Stanford, 16 Dec. 2011, \url{www.youtube.com/watch?v=3apIZCpmdls}.

%\bibitem{n}
%Craig, K. “Spring-Pendulum Dynamic System.” \emph{NYU Engineering}, \url{engineering.nyu.edu/mechatronics/Control\_Lab/Criag/Craig\_RPI/200}. Accessed 2 Aug. 2021.

%\bibitem{r}
%“Equations of Motion for the Elastic Pendulum (2DOF) Using Lagrange’s Equations.” \emph{YouTube}, uploaded by Good Vibrations with Freeball, 10 July 2020, \url{www.youtube.com/watch?v=iULa9A00JpA}.

%\bibitem{x}
%“Hamilton’s Principle and Euler-Lagrange Equations.” \emph{YouTube}, uploaded by Rangeet Bhattacharyya, 15 Sept. 2020, \url{www.youtube.com/watch?v=FBcS9RHzHRw}.

%\bibitem{y}
%Han, Yün. “ECE 486 Control Systems.” \emph{ECE 486 Control Systems - Lecture 2}, University of Illinois, 18 Jan. 2018, \url{courses.engr.illinois.edu/ece486/sp2021/documentation/handbook/lec02.html}.

%\bibitem{z}
%“Introduction to Lagrangian Mechanics.” \emph{YouTube}, uploaded by Physics Explained, 18 Oct. 2020, \url{www.youtube.com/watch?v=8UtnDaGHpq0}.

%\bibitem{ac}
%Libretexts. “10.4: Rayleigh’s Dissipation Function.” \emph{Physics LibreTexts}, 28 Feb. 2021, \url{phys.libretexts.org/Bookshelves/Classical\_Mechanics/ \\ Variational\_Principles\_in\_Classical\_Mechanics\_(Cline)/ \\ 10\%3A\_Nonconservative\_Systems/10.04\%3A\_Rayleighs\_Dissipatio\_Function}.

%\bibitem{ak}
%“Rayleigh Dissipation Function | Classical Mechanics | LetThereBeMath |.” \emph{YouTube}, uploaded by Let there be math, 24 Oct. 2017, \url{www.youtube.com/watch?v=AX\_XjLxTXWU}.

%\bibitem{am}
%“Showcase of Lagrangian Mechanics Using an Elastic Pendulum.” \emph{YouTube}, uploaded by Benedict Wesson, 24 May 2015, \url{www.youtube.com/watch?v=CA34i245meQ}.

%\bibitem{ap}
%Stanovnik, Aleš, and Borut Jurcic-Zlobec. “Numerical Study of the Elastic Pendulum on the Rotating Earth.” \emph{ISRN Mathematical Physics}, vol. 2012, 2012, pp. 1–7. \emph{Crossref}, doi:10.5402/2012/806231.

%\bibitem{ax}
%Pokorny, P. “Continuation of Periodic Solutions of Dissipative and Conservative Systems: Application to Elastic Pendulum.” \emph{Mathematical Problems in Engineering}, vol. 2009, 2009, pp. 1–15. Crossref, doi:10.1155/2009/104547.

%\bibitem{bf}
%Wylie, Clarence Raymond. \emph{Advanced Engineering Mathematics}. 4th ed., McGraw-Hill, 1975.

\end{thebibliography}


